High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-12-08 Draft_V4046Sgr_mnras.tex
SC edits

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc
  known for its wide cavity and dusty ring.  We present high
  resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm
  continuum which, combined with SPHERE-IRDIS polarized images and a
  well-sampled spectral energy distribution (SED), allow us to propose
  a physical model for the source using radiative transfer (RT)
  predictions.  The new ALMA data reveal a very thin ring at a radius
  of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial
  width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a
  $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer
  ring (Ring24) with a sharp inner edge at 24\,au. The steeply
  decreasing brightness of Ring24 breaks at $\sim$35\,au into a
  shallow tail. In order to reproduce the SED, the model that we
  popose requires an inner ring at $\sim$6\,au (Ring6) in small dust
  grains, hiding under the IRDIS coronagraph, and that surrounds an
  inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02 $
  ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
  The surprisingly thin Ring13 is nonetheless roughly 5 times wider
  than the model scale height, and could thus be long-lived. The
  strong near-far disc asymmetry at 1.65\,$\micron$ points at a very
  forward-scattering phase function, and requires grain radii of no
  less than 0.4\,$\micron$. The previously reported scattered-light
  shadow of the secondary star is also reproduced by the RADMC3D RT
  package. 
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed
current knowledge of planet formation. The focus of resolved imaging
with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
the current generation of high-contrast cameras has mainly been
towards the brighter sources
\citep[e.g.][]{Andrews2020arXiv200105007A} ***update to journal
citation***. It is to address this bias that the programme called
``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected
differential polarization imaging (DPI) data secured with the
Spectro-Polarimeter High-contrast Exoplanet REsearch
\citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type
stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased
towards exceptionally bright and large discs. The DARTTS observations
revealed diverse structures and morphologies in the scattering surface
of these discs. This letter on V4046 Sagittarii (Sgr) is part of a
companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al. {\em in prep}), which
will present millimetre observations of nine protoplanetary discs
previously imaged in polarized scattered light in DARTTS-S.

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5
and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and
0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} ***DID ROSENFELD+
PERFORM THESE MEASUREMENTS? IF NO USE CORRECT REFERENCE***, on a close
($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital
period of 2.42 days \citep{refId0}. It is a member of the $\beta$
Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of
23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is
72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive
($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au
\citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.

@@

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S. Perez).  The observations  acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with  (i.e. with a  band 6 211-275\,GHz correlator setup). The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$, in  natural weights. Here we focus on the continuum observations only.

V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}. Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.

Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
\begin{equation}
  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
\end{equation}
The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
\begin{equation}
S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
\end{equation}
where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$). Here we set $\lambda = 0.01$.  Similar applications of {\tt uvmem} in the context of protoplanetary disks can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.  An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}. This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.

The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$) ***NOT THE SAME BEAM AS IN THE TEXT****, and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$) ***NOT 1/3 OF THE BEAM.... NOT THE FIRST TIME THIS IS NOTICED, PLEASE FIX FOR GOOD****. The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: synthetic image at 1.65\,$\upmu m$. Bottom right panel: synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}. We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al. (2021, in prep). The resulting disk orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars. ***PLEASE MAKE SURE THESE ARE THE FINAL AND CORRECT NUMBERS**** The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case. ***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ****

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.  ***MAKE SURE ALL NUMBERS ARE CONSISTENT****

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system ****REPLACE WITH ESTIMATE OF THE RADIUS OF THIS CENTRAL BLOB, USE AN ELLIPTICAL GAUSSIAN FIT****, and may be part of inner disk introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

@@

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

For  stars were modeled using  two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/5 for simplicity ***(now is not for simplicity) OK SO EXPLAIN FURTHER *****.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indexes $\psi$. The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. The total gas surface density is then  given  by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disk follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.

We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both  components separately.

For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$. But the inner wall of Ring24 follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the model large-grain density at 64\,au. The large-dust surface density profile is defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

>>>>

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas **** WRONG UPDATE TO CORRECT NUMBERS****) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The intensity plateau in Ring24 breaks at $\sim$35\,au, where it steeply drops  and  extends into  a shallow tail. A compact source of mm-continuum at  the stellar position is picked up by ALMA, with a radius of ***RADIUS OF THE BLOB, IS IT RESOLVED?***.  In order to reproduce the SED in the IR, our RT model  requires an  inner circumbinary disc ***GIVE RADII*** rich in small grains (as in previous  models of V4046\,Sgr), and  which  matches the  central ALMA signal if it contains **Xxx*** Mearths in large dust. An inner  ring at $\sim$6\,au (Ring6) composed of small  grains, with a gas mass of ***Mearth*** and deprived of large dust, is required to explain the ***10$\mu$m ???*** flux density. The surprisingly thin Ring13 is nonetheless $\sim$5 times wider ****NOT CONSISTENT WITH CONCLUSIONS*** in the ALMA signal  than the model scale height, and $\sim$3***???*** narrower than the model gas radial width. Ring13 could thus be   long-lived and shaped by radial dust trapping, which would require a turbulence value of  $\alpha_{\rm turb} \sim 0.01$.   The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package. 
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed current knowledge of planet formation. The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}. It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased towards exceptionally bright and large discs. The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs. This letter on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al. {\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.

@@

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S. Perez).  The observations  acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with  (i.e. with a  band 6 211-275\,GHz correlator setup). The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs062 \,\times \, 0\farcs055$, in  natural weights. Here we focus on the continuum observations only.

V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE-IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}. Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.

Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
\begin{equation}
  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 - \lambda S.
\end{equation}
The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
\begin{equation}
S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
\end{equation}
where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$). Here we set $\lambda = 0.01$.  Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.  An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}. This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.

The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr. \textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image. ***NO YELLOW ELLIPSE?*** The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$ **WRONG***). The inset zooms into the central emission, and the green star marks the binary position. \textit{Bottom left panel:} synthetic image at 1.65\,$\micron$. \textit{Bottom right panel:} synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}. We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al. (2021, in prep). The resulting disc orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars. The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case. ***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ***

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

@@

The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1. The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure to reproduce the observations. We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}

We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.

For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
The inner edge of Ring24 follows a different profile. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the profile of large dust grains at 64\,au. It is then defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}
